%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Long Sectioned Curriculum Vitae
% LaTeX Template
%
% This template has been downloaded from:
% http://www.latextemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{res} % Use the res.cls style
\usepackage{xcolor}
\newcommand\crule[3][black]{\textcolor{#1}{\rule{#2}{#3}}}
\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\newsectionwidth{0pt} % Stops section indenting

\begin{document}

%----------------------------------------------------------------------------------------
%	YOUR NAME AND ADDRESS(ES) SECTION
%----------------------------------------------------------------------------------------

\name{Rudrasis Chakraborty\\ \\} % Your name at the top

% If you don't want one of the addresses, simply remove all the text in the first or second \address{} bracket

\address{{\bf Current Affiliation} \\ Graduate Student, CISE \\ University of Florida, Gainesville \\Florida 32605, USA} % Your address 1
%{\bf School Address} \\ Department of Study \\ University \\ City, State 12345 \\ (000) 111-1111
\address{{\bf Address} \\ 2811 SW Archer Road\\ Gainesville\\ FL 32608 \\ (+1) 352-871-4938 \\ rudrasischa AT gmail DOT com} % Your address 2

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------

%\section{\centerline{OBJECTIVE}}

%\vspace{8pt} % Gap between title and text

%A position in Personnel Administration utilizing skills in recruiting, training and compensation.\\ 

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{EDUCATION}} 

\vspace{8pt} % Gap between title and text

{\sl Graduate Student},
Computer \& Information Science \& Engg. \\
University of Florida, USA \hfill Aug. 2013 - \\
SUPERVISOR - Prof. Baba C. Vemuri \\
CGPA - 3.94


{\sl Master of Technology}, 
Computer Science \& Engg. \\ 
Indian Statistical Institute, Kolkata, India \hfill 2010-2012 \\ 
THESIS - Incorporating $\epsilon$-dominance in MultiObjective Optimization : A study in AMOSA \\
SUPERVISOR - Prof. Sanghamitra Bandyopadhyay \\
Percentage 88.16 (1st class Distinction)
 
{\sl Bachelor of Engineering},
Computer Science \& Engg. \\ 
Jadavpur University, Kolkata, India \hfill 2006-2010 \\
THESIS - Audio Classification \\
SUPERVISOR - Dr. Sanjoy Kumar Saha \\
CGPA 8.68 (1st class Hons.)

%{\sl Bachelor of Science}, Psychology \\ 
%Utica College of Syracuse University, Utica, NY \hfill May 1987

%----------------------------------------------------------------------------------------
 
\vspace{0.2in} % Some whitespace between sections
%
%%----------------------------------------------------------------------------------------
%%	RESEARCH EXPERIENCE SECTION
%%----------------------------------------------------------------------------------------
%
%\section{\centerline{RESEARCH EXPERIENCE}} 
%
%\vspace{8pt} % Gap between title and text
%
%
%{\sl Dimensionality Reduction Problem} \hfill August 2012 -- ongoing \\
%SUPERVISOR : Dr. Nikhil R. Pal \\
%AFFILIATION : Professor, Indian Statistical Institute, Kolkata, India
%\begin{itemize}
%\item Dimensionality Reduction Problem
%\end{itemize}
%
%{\sl Sensor Selection} \hfill June 2012 -- ongoing \\
%SUPERVISOR : Dr. Nikhil. R. Pal \\
%AFFILIATION : Professor, Indian Statistical Institute, Kolkata, India
%\begin{itemize}
%\item Selection of sensors (group feature) with controlled redundancy and its real life application.
%\end{itemize}
%
%{\sl Dimensionality Reduction} \hfill 2011 -- 2012 \\
%SUPERVISOR : Dr. Nikhil. R. Pal \\
%AFFILIATION : Professor, Indian Statistical Institute, Kolkata, India
%\begin{itemize}
%\item Develop a redundancy controlled dimensionality reduction technique based on neural network.
%\end{itemize}
%
%{\sl Word Segmentation and and Policy Evaluation} \hfill May 2011 -- July 2011 \\
%MENTOR : Sourangshu Bhattacharya \\
%AFFILIATION : Senior Research Scientist, Yahoo! R $\&$ D labs, Bangalore.
%\begin{itemize}
%\item Word segmentation on web urls.
%\item Policy evaluation in contextual bandit problem.
%\end{itemize}
%
%
%{\sl MultiObjective Optimization} \hfill 2009 -- 2012 \\
%SUPERVISOR : Dr. Sanghamitra Bandyopadhyay \\
%AFFILIATION : Professor, Indian Statistical Institute, Kolkata, India
%\begin{itemize} \itemsep -2pt % Reduce space between items
%\item Introduce $\epsilon$-dominance in popular multiobjective algorithm AMOSA and study the performance on benchmark problems and real life clustering application.
%\item Develop a novel priority based $\epsilon$-dominance and study the improvement after incorporating it into exisitng MOO algorithms.
%\end{itemize}
% 
%
%{\sl Audio Classification} \hfill 2009 -- ongoing \\
%SUPERVISOR : Dr. Sanjoy Kumar Saha \\
%AFFILIATION : Associate Professor, Jadavpur University, Kolkata, India
%\begin{itemize} \itemsep -2pt % Reduce space between items
%\item Classification of Speech and Non-Speech signal, then further classify non-speech into instrument and song.
%\item Classify different instrument type like Drum, Sitar, Piano, Tabla etc.
%\item Classification of several song genres like Pop, Rock, Jazz etc. (ongoing).
%\item Segment one signal into constituent Instrument, Song and Speech segments (ongoing).
%\end{itemize}
%
%
%
%%----------------------------------------------------------------------------------------
%
%\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION
%----------------------------------------------------------------------------------------
\section{\centerline{Publications}}
\vspace{2pt}
{\bf Legend:} \footnotesize{\crule[cyan]{0.2cm}{0.2cm} Machine Learning, \crule[red!50!white!100]{0.2cm}{0.2cm} Diff. Geometry, \crule[blue]{0.2cm}{0.2cm} Statistics, \crule[green!50!white!100]{0.2cm}{0.2cm} Signal Processing, \crule[brown]{0.2cm}{0.2cm} Evolutionary Computation, \crule[magenta]{0.2cm}{0.2cm} Computer Vision, \crule[yellow]{0.2cm}{0.2cm} Medical Imaging}    
\vspace{0.2in}

\section{\centerline{Publications during PhD}} 
\vspace{5pt} % Gap between title and text
\begin{itemize}
\item ``Recursive Frechet Mean Computation on the Grassmann and its Applications to Computer Vision", \textbf{Rudrasis Chakraborty} and B. Vemuri, ICCV, 2015. \crule[red!50!white!100]{0.2cm}{0.2cm} \crule[blue]{0.2cm}{0.2cm} \crule[magenta]{0.2cm}{0.2cm}
\item ``An efficient recursive algorithm for atlas construction", \textbf{Rudrasis Chakraborty}, M. Banerjee, D. Seo, S. Turner, D. Fuller, J. Forder and B. Vemuri, MICCAI workshop on Mathematical Foundations of Computational Anatomy (MFCA), 2015. \crule[red!50!white!100]{0.2cm}{0.2cm} \crule[blue]{0.2cm}{0.2cm} \crule[yellow]{0.2cm}{0.2cm}
\item ``An efficient recursive estimator of the Fr{\'e}chet mean on hypersphere with applications to Medical Image Analysis", H. Salehian,  \textbf{Rudrasis Chakraborty}, E. Ofori, D. Vaillancourt and B. Vemuri, MICCAI workshop on Mathematical Foundations of Computational Anatomy (MFCA), 2015. \crule[red!50!white!100]{0.2cm}{0.2cm} \crule[blue]{0.2cm}{0.2cm} \crule[yellow]{0.2cm}{0.2cm}
\item ``Nonlinear regression on Riemannian manifolds and its applications to Neuro-image analysis", M. Banerjee, \textbf{Rudrasis Chakraborty}, D. Villiancourt, E. Ofori and B. Vemuri, MICCAI, 2015. \crule[red!50!white!100]{0.2cm}{0.2cm} \crule[blue]{0.2cm}{0.2cm} \crule[yellow]{0.2cm}{0.2cm}
\end{itemize}

\vspace{0.2in} % Some whitespace between sections

\section{\centerline{Publications during Master}} 
\vspace{5pt}
\begin{itemize}
\item ``Sensor (Feature-Group) Selection with Controlled Redundancy in a Connectionist Framework'', \textbf{Rudrasis Chakraborty}, C. T. Lin and Nikhil R. Pal in International Journal of Neural Systems, 24(6), 2014, \emph{IF: 6.507}. \crule[cyan]{0.2cm}{0.2cm}
\item ``A New Measure of Priority Based $\epsilon$ Dominance in Multiobjective Optimization'', S. Bandyopadhyay, \textbf{Rudrasis Chakraborty} and U. Maulik  in Information Sciences, 305, 2015, \emph{IF: 4.038}. \crule[brown]{0.2cm}{0.2cm}
\item ``Feature Selection Using a Neural Framework with Controlled Redundancy'', \textbf{Rudrasis Chakraborty} and Nikhil R. Pal in IEEE Transaction in Neural Network and Learning Systems, 26(1), 2015 \emph{IF: 4.291}. \crule[cyan]{0.2cm}{0.2cm}
\item ``Incorporating $\epsilon$-dominance in AMOSA: Application to multiobjective 0/1 knapsack problem and clustering gene expression data", S. Bandyopadhyay, U. Maulik, \textbf{Rudrasis Chakraborty} in Applied Soft Computing, Vol. 13, No. 5, May 2013, 2405 - 2411 \emph{IF: 2.810}. \crule[brown]{0.2cm}{0.2cm}

\end{itemize}

\vspace{0.2in} % Some whitespace between sections

\section{\centerline{Publications during Bachelor}} 
\vspace{5pt}
\begin{itemize}
\item ``Perceptual Feature Based Song Genre Classification using RANSAC'', A. Ghoshal, \textbf{Rudrasis Chakraborty}, B. Chanda Dhara, S. K. Saha in International Journal of Computational Intelligence Studies, 4(1), 2015. \crule[green!50!white!100]{0.2cm}{0.2cm}
\item ``A hierarchical approach for speech-instrumental-song classification'', A. Ghoshal, \textbf{Rudrasis Chakraborty}, B. Chanda Dhara, S. K. Saha in Springer Plus 2013, 2:526. \crule[green!50!white!100]{0.2cm}{0.2cm}
\item ``Music Classification Based on MFCC Variants and Amplitude Variation Pattern: A hierarchical approach", A. Ghoshal, \textbf{Rudrasis Chakraborty}, B. Chanda Dhara, S. K. Saha in International Journal of Signal Processing, Image Processing and Pattern Recognition (IJSIP), Vol.5, No.1, March 2012. \crule[green!50!white!100]{0.2cm}{0.2cm}
\item ``Genre Based Classification of Song Using Perceptual Features", A. Ghoshal, \textbf{Rudrasis Chakraborty}, B. Chanda Dhara, S. K. Saha in International Conference on Advanced Computing, Networking, and Informatics, 2013. \crule[green!50!white!100]{0.2cm}{0.2cm}
\item ``Segmenting Web-Domains and Hashtags using Length Specific Models", S. Srinivasan, S. Bhattacharya, \textbf{Rudrasis Chakraborty} in 21st ACM International Conference on Information and Knowledge Management (CIKM), 2012. \crule[cyan]{0.2cm}{0.2cm}
\item ``Song/Instrumental Classification using Spectrogram Based Contextual Features", A. Ghoshal, \textbf{Rudrasis Chakraborty}, B. Chanda Dhara, S. K. Saha in CUBE International Conference, 2012. \crule[green!50!white!100]{0.2cm}{0.2cm}
\item ``Song Classification: Classical and Non-classical Discrimination using MFCC Co-occurrence Based Features'', A. Ghoshal, \textbf{Rudrasis Chakraborty}, B. Chanda Dhara, S. K. Saha in International Conference of Signal Processing, Image Processing and Pattern Recognition (SIP), 2011. \crule[green!50!white!100]{0.2cm}{0.2cm}
\item ``Automatic Identification of Instrument Type in Music Signal using Wavelet and MFCC'', A. Ghoshal, \textbf{Rudrasis Chakraborty}, B. Chanda Dhara, S. K. Saha in Fifth International Conference on Information Processing (ICIP), 2011. \crule[green!50!white!100]{0.2cm}{0.2cm}
\item ``Instrumental/Song Classification of Music Signal Using RANSAC'', A. Ghoshal, \textbf{Rudrasis Chakraborty}, B. Chanda Dhara, S. K. Saha in 3rd International Conference on Electronics Computer Technology (ICECT), 2011. \crule[green!50!white!100]{0.2cm}{0.2cm}
\item ``Speech/Music Classification Using Occurrence Pattern of ZCR and STE'', A. Ghoshal, \textbf{Rudrasis Chakraborty}, R. Chakraborty, S. Haty, B. Chanda Dhara, S. K. Saha in 3rd International Conference on Intelligent Information Technology Application (IITA), 2009. \crule[green!50!white!100]{0.2cm}{0.2cm}
\end{itemize}

%\vspace{0.2in} % Some whitespace between sections


%\section{\centerline{COMMUNICATED MANUSCRIPTS}} 

%\vspace{15pt} % Gap between title and text
%\begin{itemize} \itemsep -2pt % Reduce space between items



%\end{itemize}


\vspace{0.2in} % Some whitespace between sections


\section{\centerline{COURSES COMPLETED}}

\vspace{8pt} % Gap between title and text
\begin{center}
Theoretical Statistics (I and II), Linear Algebra, Curves and Surfaces, Differential Geometry (I and II), Advanced Differential Geometry (I), Markov Chain Monte Carlo, Computer Vision, Medical Image Analysis, Pattern Recognition and Image Processing, Artificial Intelligence, Advanced Image Processing,  Neural Networks\\
\end{center}
%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections



%----------------------------------------------------------------------------------------
%	MEMBERSHIPS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{MEMBERSHIPS}} 

\vspace{-5pt} % Reduce space between section title and contents

\begin{center}
Graduate Student Member of IEEE \\
SIAM Student Member \\ 
\end{center}

\vspace{0.2in} % Some whitespace between sections



%----------------------------------------------------------------------------------------
%	MEMBERSHIPS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{REVIEWERSHIPS}} 

\vspace{-5pt} % Reduce space between section title and contents

\begin{center}
{\it Conferences:} ICCV 2015, CVPR 2016 \\
{\it Journals:} IEEE Tran. Cybernetics, IEEE TNNLS, IEEE TSMC-A, Information Sciences, Applied Soft Computing
\end{center}

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	HONORS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{AWARDS AND FELLOWSHIPS}} 

\vspace{-5pt} % Reduce space between section title and contents

\begin{center}
Awarded CISE travel grant to attend MICCAI 2015. \\
Graduate School Fellowship from University of Florida. \\
Gold Medal for best B.E Thesis in Jadavpur University. \\
Appear first in M.Tech Curriculum in Indian Statistical Institute. \\
ISIAA gold medal for standing first in M.Tech curriculum in Indian Statistical Institute. \\
Received award in forms of books in all the four semesters during M.Tech curriculum. \\
Awarded first prize in DST sponsored Image processing workshop held in Indian Statistical Institute, 2010. \\

\end{center}

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	HONORS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{PRESENTATION AND INVITED TALKS}} 

\vspace{-5pt} % Reduce space between section title and contents

\begin{itemize}
\item Invited talk in Indian Statistical Institute, Dec., 2015 on ``An efficient way to compute Frechet mean  on Riemannian manifold''.
\item Presented the work ``Nonlinear regression on Riemannian manifolds and its applications to Neuro-image analysis'' in MICCAI, 2015.
\item Presented the work ``An efficient recursive algorithm for atlas construction'' in MICCAI sponsored workshop MFCA, 2015.
\item Presented the work ``An efficient recursive estimator of the Fr{\'e}chet mean on hypersphere with applications to Medical Image Analysis'' in MICCAI sponsored workshop MFCA, 2015.


\end{itemize}

%----------------------------------------------------------------------------------------


\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	HONORS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{INTERNSHIPS \& WORK EXPERIENCES}} 

\vspace{-5pt} % Reduce space between section title and contents

\begin{center}
Indian Statistical Institue, Kolkata  \hfill May 2009 -- July 2009 \\
Yahoo! R \& D Labs, Bangalore \hfill May 2011 -- July 2011 \\
Teaching Assistant of Data Structure using C++, University of Florida \hfill August 2013 - Present  \\
\end{center}

%----------------------------------------------------------------------------------------


\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{INTERESTS}} 

\vspace{-5pt} % Reduce space between section title and contents

\begin{center}
Differential Geometry, Computer Vision, Patter Recognition, Listening Music, Artificial Intelligence, Reading Books, Information Theory, Signal Processing, Fishing, Neural Network
\end{center} 

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections


\section{\centerline{SKILLS}}

\vspace{8pt} % Gap between title and text
\begin{center}
\begin{itemize}
\item Operating Systems : Linux, Microsoft Windows 
\item Programming Languages : C, C++, Java, Python
\item Software Packages : MATLAB, \LaTeX
\end{itemize}
\end{center}
%----------------------------------------------------------------------------------------


\end{resume} 
\end{document}
